Context-dependent consequences of including lagged effects in demographic models

### 2022-04-20 docs/paper.Rmd
draft CRediT statement
add table of lambdas and reference to results text

For all vital rates estimated using the long term demographic dataset, the DLNM model fit the best (dAIC = 0) followed by the model with a random effect of year, followed by the deterministic model (Table \@ref(tab:aic))

-   table of vital rate models.
    Which vital rate, which IPM, ∆AIC, model edf.

-   table of lambdas.
    2 habitats x 3 (4?) IPMs

-   figure of PVA??
    Conceptual diagram instead?

@@

@@

@@

>>>>

For all vital rates estimated using the long term demographic dataset, the DLNM model fit the best (dAIC = 0) followed by the model with a random effect of year, followed by the deterministic model (Table \@ref(tab:aic)).

Population growth rates were consistently higher in continuous forest compared to forest fragments across IPM types (Table \@ref(tab:lambdas)).

@@

ERS contributed to the conceptualization, methodology, formal analysis, and led the writing of the original draft.
EMB contributed to the conceptualization, methodology, and writing and also acquired funding.

@@

```{r lambdas, results='asis'}
pandoc.table(
  tar_read(lambda_table),
  digits = 5,
  keep.trailing.zeros = TRUE,
  justify = c("left", "left", "right", "right", "right", "right"),
  full_width = FALSE,
  caption = "(\\#tab:lambda) Population growth rates for continuous forest (cf) and forest fragments (ff) under different kinds of IPMs with bootstrapped 95% confidence intervals."
)

```

@@

Some kind of conceptual diagram of the methods?
The life cycle diagram with equations on it?
